\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-09 paper.tex
IROS review: clarify relation with BDI

Our architecture relates but is to be distinguished from \emph{Beliefs,
Desires, Intentions} (BDI) architectures. BDI architectures are primarily
focused on \emph{practical reasoning}, \ie the process of deciding, step by
step, which action to perform to reach a goal (as summarised by
Woolridge~\cite{Woolridge1999}). The management of the interaction between
knowledge (the beliefs) and task and plan representation and execution (the
desires and the intentions) is central, and aims at selecting at each step the
best subgoal. It becomes then an intention that the robot commits to.

This interaction between knowledge and actions is also central to our approach
(as for any cognitive system), but task representation and task execution is
not seen as a monolithic, central function: it is one of the activities of the
robot, actually split between communication components (that can acquire
desires from interaction with agents, amongst other things) and an execution
controller that may decide to take an incoming desire into account to create
its own internal goals. The controller generates and manages intentions from
these goals with the help of a symbolic task planner, that also has direct
access to the knowledge base.

The architecture is not only focused on this workload, and other
activities are conducted without being explicitly considered as desires:
assessment of the situation and the environment, dialogue (including
performative dialogue that can possibly change the internal state of the robot,
but does not lead to the creation of desires,  like question answering or
statement assertion), various background monitoring and recognition tasks, etc.

@@

\subsection{Knowledge model}

>>>>

Our architecture relates to \emph{Beliefs, Desires, Intentions} (BDI)
architectures. BDI architectures are primarily focused on \emph{practical
reasoning}, \ie the process of deciding, step by step, which action to perform
to reach a goal (as summarised by Woolridge~\cite{Woolridge1999}). The
management of the interaction between knowledge (the beliefs) and task and plan
representation and execution (the desires and the intentions) is central, and
aims at selecting at each step the best subgoal. It becomes then an intention
that the robot commits to.

This interaction between knowledge and actions is also central to our approach
(as for any cognitive system): it is one of the activities of the
robot, actually shared between communication components (that can acquire
desires from interaction with agents, amongst other things) and an execution
controller that may decide to take an incoming desire into account to create
its own internal goals. The controller generates and manages intentions from
these goals with the help of a symbolic task planner, that also has direct
access to the knowledge base.

Our architecture is however \emph{not built around} this activity only. Other
activities are conducted in parallel, without being explicitly considered as
desires: assessment of the situation and the environment, dialogue (including
performative dialogue that can possibly change the internal state of the robot,
but does not lead to the creation of desires,like question answering or
statement assertion), various background monitoring and recognition tasks, etc.

@@

\subsection*{Knowledge model}
